Figures for Paper

### 2021-09-22 paper_figures.Rmd

ggplot(df2, aes(x = experiment, fill = RNA, y = mean_kd)) +
    geom_bar(stat="identity", position="dodge") +
    #geom_point(aes(group=RNA), position="dodge") +
    geom_errorbar(aes(x=experiment, ymin = mean_kd-sd2, ymax = mean_kd+sd2,
                      fill = RNA), position="dodge") +
    ylim(0, NA) +
    ggpubr::theme_pubr() +
    ylab("Kd / nM") +
    xlab("")

t.test(df$kd[which(df$RNA=="H" & df$experiment=="exon")], df$kd[which(df$RNA=="R" & df$experiment=="exon")])
t.test(df$kd[which(df$RNA=="H" & df$experiment=="intron")], df$kd[which(df$RNA=="R" & df$experiment=="intron")])  # this is an overestimate of significance - however still borderline significant (~0.05) when fitting error is taken into account
```

>>>>

ggplot(df2, aes(x = experiment, fill = RNA, y = mean_kd)) +
    geom_bar(stat="identity", position="dodge") +
    geom_errorbar(aes(x=experiment, ymin = mean_kd-sd2, ymax = mean_kd+sd2,
                      fill = RNA), position="dodge") +
    ylim(0, NA)  +
    geom_jitter(data = df, 
                aes(group=RNA,x = experiment, y = kd,fill = RNA), 
                position=position_jitterdodge(jitter.width = 0.1),pch = 21,size = 3,) +
    ggpubr::theme_pubr() +
    ylab("Kd / nM") +
    xlab("") +
  scale_fill_manual(values = c("#0c9bbdff","#ffb700ff"))

exon_pval = t.test(df$kd[which(df$RNA=="H" & df$experiment=="exon")], df$kd[which(df$RNA=="R" & df$experiment=="exon")]) %>% broom::tidy() %>% pull(p.value)
intron_pval = t.test(df$kd[which(df$RNA=="H" & df$experiment=="intron")], df$kd[which(df$RNA=="R" & df$experiment=="intron")])  %>% broom::tidy() %>% pull(p.value) # this is an overestimate of significance - however still borderline significant (~0.05) when fitting error is taken into account
```

P-value two sample t-test:

* RE - `r exon_pval`
* RI - `r intron_pval`

# Expression of ALS/FTD risk genes
